Space transformation in Multidimensional IRT (Lemmas)

### 2022-08-11 notebooks/Space_transformation_theorem.qmd
Final transcriptions of Mario's lemmas about the direction cosines

>>>>

There is little difference (notation and a few steps) from my own computataions,
so I think its ok not to transcribe it (Mario and I are "on the same page").

# Test space and latent space

I think this part details the derivation of my Equation 21 (which I have
omitted, but is equivalent to Equations 13 through 15), so it is ok not to
transcribe this part for now.
